The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-04-15 Article/Article20140406Granada/LatexArt/article_main.tex
effectiveness
titlerunning - The investment strategy based on behavior of artificial earthworm
in the Matlab

% a short form should be given in case it is too long for the running head
\titlerunning{SHORT TITLE}

@@

Described algorithm is implemented the in Matlab and using the platform Metatrader MQL4 language. The study was conducted both in the historical data (of course with the principles of machine learning --- testing was carried out using data not used in the learning phase) and a real ,,live'' market. Between the communities, there are also important differences that affect the diversity of simulation results.

@@

In addition, efficacy studies were carried out and optimized for different test periods. To these results can be compared with each other, has been carried out their link, and the results were divided by the length of the test period, expressed by the number of candles. 
Figure \ref{fig:fig10} and Figure \ref{fig:fig11} present the results.

>>>>

% a short form should be given in case it is too long for the running head
\titlerunning{The investment strategy based on behavior of artificial earthworm}

@@

Described algorithm is implemented in the Matlab and using the MQL4 language of the Metatrader platform. The study was conducted both in the historical data (of course with the principles of machine learning --- testing was carried out using data not used in the learning phase) and a real ,,live'' market. Between the communities, there are also important differences that affect the diversity of simulation results.

@@

In addition, effectiveness studies were carried out and optimized for different test periods. To these results can be compared with each other, has been carried out their link, and the results were divided by the length of the test period, expressed by the number of candles. 
Figure \ref{fig:fig10} and Figure \ref{fig:fig11} present the results.
